NumPy---Array Computation for Python

### 2020-01-04 summary.tex
Minor edits

% - 2-3 sentences of basic-level introduction to the field;
Software libraries for array computation provide powerful notation
for accessing, manipulating, and operating on aggregate data \cite{iverson1980notation}.
% - a brief account of the background and rationale of the work;
NumPy is the fundamental array computation library for the Python ecosystem
\cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
Not surprisingly, many important scientific research projects and results
crucially rely on NumPy.
It plays an essential role in many research analysis pipelines in fields as
diverse as physics, biology, astronomy, neuroscience, material science,
engineering, and chemistry.
In particular, NumPy played a fundamental role in discovering gravitational
waves\cite{pycbc} and the first imaging of a black hole\cite{eht-imaging}, and
lets us explore our universe\cite{jenness2018lsst}.
It is one of the most commonly used machine learning tools among enterprises
\cite{451report2018}.
% - a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
Here we provide an overview of the project and library organization,  highlight
some recent technical developments, and outline our future plans.
% - 2-3 sentences putting the main findings into general context so it is
%   clear how the results described in the paper have moved the field forwards.
NumPy continues to evolve to meet the needs of its community, to remain
relevant in an ever-changing computing landscape, and to be a fundamental
pillar of support for the next decade of data science in Python.

>>>>

% - 2-3 sentences of basic-level introduction to the field;
Software libraries for array computation provide powerful notation
for accessing, manipulating, and operating on aggregate data in vectors,
matrices, or higher-dimensional arrays \cite{iverson1980notation}.
% - a brief account of the background and rationale of the work;
NumPy is the fundamental array computation library for the Python ecosystem
\cite{dubois2007guest,oliphant2007python,millman2011python,perez2011python}.
Not surprisingly, many important scientific research projects and results
crucially rely on NumPy.
It plays an essential role in many research analysis pipelines in fields as
diverse as physics, biology, astronomy, neuroscience, material science,
engineering, and chemistry.
In particular, NumPy played a fundamental role in discovering gravitational
waves\cite{pycbc} and the first imaging of a black hole\cite{eht-imaging}, and
lets us explore our universe\cite{jenness2018lsst}.
It is also one of the most commonly used machine learning tools among
enterprises \cite{451report2018}.
% - a statement of the main conclusions (introduced by the phrase 'Here we show' or its equivalent);
Here we provide an overview of the project and library organization,  highlight
some recent technical developments, and outline our future plans.
% - 2-3 sentences putting the main findings into general context so it is
%   clear how the results described in the paper have moved the field forwards.
NumPy continues to evolve to meet the needs of its community, to remain
relevant in an ever-changing computing landscape, and to be a fundamental
pillar of support for the next decade of data science in Python.
